---
title: "tidytuesday"
description: |
  A short description of the post.
author:
  - name: Arthur Gailes
    url: {}
date: 01-26-2021
output:
  distill::distill_article:
    self_contained: false
draft: true
---


A quick demonstration of affline transformations with the Kenya Census

## Data Source

Thanks as always to the [TidyTuesday crew at R4DS](https://github.com/rfordatascience/tidytuesday).

The data this week comes from [Break Free from Plastic courtesy of Sarah Sauve.](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-01-26/readme.md)


# Load the weekly Data


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=F)
sapply(c('tidyverse','tidytuesdayR','here','ggplot2','ggthemes','sf', 'r2d3',
  'gganimate'), require, character.only=T)
# distill seems to use the project directory rather than the file directory.
knitr::opts_knit$set(root.dir = paste0(here(),'/_posts/2021-01-26-tidytuesday/'))
# setwd is not canonical, but works for me for some reason.
setwd(paste0(here(),'/_posts/2021-01-26-tidytuesday/'))
```


```{r Readme, eval = interactive(), include=FALSE}
tt <- tt_load("2021-01-26")
tt


tt %>% 
  map(glimpse)
```


Dowload the weekly data and make available in the `tt` object. Use the rKenyaCensus to do so, adding the polygons for each county.

```{r download, eval=FALSE}
plastic <- tt_load("2021-01-26")$plastic
write_csv(plastic, 'plastic.csv')
```


After saving, load from the directory directly:

```{r Load}
plastic <- read_csv('plastic.csv')

```


# Glimpse Data

Take an initial look at the format of the data available.


```{r}
head(plastic)

```


# Wrangle

Transform to long by recycling code:
```{r}
plast_reduce <- plastic %>% 
  filter(year==2020, !parent_company %in% c('Unbranded','null','NULL')) %>% 
  select(country, parent_company, grand_total) %>% 
  # get the total for each company by country
  group_by(country, parent_company) %>% 
  summarize(grand_total = sum(grand_total, na.rm=T), .groups='drop_last') %>% 
  # keep only the top company in eac h country
  filter(grand_total == max(grand_total)) %>% ungroup() %>% 
  arrange(desc(grand_total))

head(plast_reduce)
```

There are `r length(unique(plast_reduce$parent_company))` total companies in the `r nrow(plast_reduce)` countries listed.

## TODO
Download one logo
Download county shapefiles
download country xwalk
Try to use it in d3 map
Download all logos if true, if false, dl top ~10 logos
* might also want top polluting countries if using cartogram/bubble map
create spreadsheet of companies + logo paths
Create pollution map
# Visualization

## Spatial Data

Load global countries geojson (downloaded from https://geojson-maps.ash.ms/).
```{r}
geo <- st_read('world_countries.geo.json') 

# create centroids
geo_cen <- st_centroid(st_transform(geo, 3857))


```


##Visualization 

It's at this point, where, if you've worked with d3 before, that you might think, "Arthur, you sweet, simple fool. D3 isn't goint to natively work with a completely unrelated R package." Well, hold on to your butts!


#### Step 1: Get a global map
```{r}
step1 <- r2d3(data=geo, script='plasticMap_step1.js', viewer='external')

step1
```

Not the prettiest map, but we're going somewhere. Now, I want to see if I can replace a polygon with an image.

```{r}
# load table of company images
logos <- read_csv('company_logos.csv')

# join with country geographies and remove extra information
geo_logo <- geo %>% 
  select(name, name2=admin, name_long, pop_est, gdp_md_est) %>% 
  mutate(name_id = tolower(name), name_id = gsub(' ','_',name_id)) %>% 
  left_join(plast_reduce, by = c('name'='country')) %>% 
  # 60 of 63 countries join. Leaving that alone for now
  left_join(logos, by=c('parent_company'='company'))

head(geo_logo)
```


#### Step 2: Place an image in the map polygons

Next, test to see if I can replace a polygon with an image.

(I tried to link this image locally, but failed. After playing with `htmlDependency` for far too long, I gave up and just added logos to the github repository.)
```{r}
# geo_test <- filter(geo_logo, parent_company == 'Universal Robina Corporation') %>% 
#   # create id for image
#   mutate(imageId = paste0('d3-', gsub(' ','', parent_company)))

r2d3(data=geo, script='plasticMap_step2.js', viewer='external')
```

Harumph. The code works, but r2d3 doesn't want to play nicely with my local images. After playing with `htmlDependency` for far too long, I gave up and just added logos to the github repository.

Okay! Not great, but we've got a logo on top of a map.

#### Step 3: Get the logo to show by country.
```{r}
# geo_test <- filter(geo_logo, parent_company == 'Universal Robina Corporation') %>% 
#   # create id for image
#   mutate(imageId = paste0('d3-', gsub(' ','', parent_company)))

r2d3(data=geo_logo, script='plasticMap_step3.js', viewer='browser')
```



#### Step 4: Show all logos

#### Step 5: Finishing Touches

# Save
```{r eval=FALSE}
anim_save('_tidytuesday/2021-01-19-tidy-tuesday/kenya_county_size.gif', anim)
```

# Review

An obvious limitation to this approach is that a polygon can only go up to 100% of its original size without exceeding its original boundaries. In this map, the smallest county has the largest population, so the visual impact of the shifts is really messy. A possible cleanup strategy would be to make the original polygons to make them smaller, and so that the population-scaled polygons could increase to fit to the original boundaries.

```{r}
r2d3(data=matrix(round(runif(16, 1, 10000)), ncol = 4, nrow = 4), script="https://raw.githubusercontent.com/rstudio/r2d3/master/vignettes/gallery/chord/chord.js")
```


# Notes
cartogram resize: https://observablehq.com/@d3/non-contiguous-cartogram
fill svg: https://stackoverflow.com/questions/3796025/fill-svg-path-element-with-a-background-image
  https://stackoverflow.com/questions/25881186/d3-fill-shape-with-image-using-pattern