---
title: "tidytuesday"
description: |
  A short description of the post.
author:
  - name: Arthur Gailes
    url: {}
date: 01-26-2021
output:
  distill::distill_article:
    self_contained: false
draft: true
---


A quick demonstration of affline transformations with the Kenya Census

## Data Source

Thanks as always to the [TidyTuesday crew at R4DS](https://github.com/rfordatascience/tidytuesday).

The data this week comes from [Break Free from Plastic courtesy of Sarah Sauve.](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-01-26/readme.md)


# Load the weekly Data


```{r setup, resutls='hide', message=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=F)
sapply(c('tidyverse','tidytuesdayR','here','ggplot2','ggthemes','sf', 'r2d3',
  'gganimate'), require, character.only=T)
# knitr::opts_knit$set(root.dir = here())
```

```{r Readme, eval = interactive(), include=FALSE}
tt <- tt_load("2021-01-26")
tt


tt %>% 
  map(glimpse)
```


Dowload the weekly data and make available in the `tt` object. Use the rKenyaCensus to do so, adding the polygons for each county.

```{r download, eval=FALSE}
plastic <- tt_load("2021-01-26")$plastic
write_csv(plastic, 'plastic.csv')
```


After saving, load from the directory directly:

```{r Load}
plastic <- read_csv('plastic.csv')

```


# Glimpse Data

Take an initial look at the format of the data available.


```{r}
head(plastic)

```


# Wrangle

Transform to long by recycling code:
```{r}
plast_reduce <- plastic %>% 
  filter(year==2020, !parent_company %in% c('Unbranded','null','NULL')) %>% 
  select(country, parent_company, grand_total) %>% 
  # get the total for each company by country
  group_by(country, parent_company) %>% 
  summarize(grand_total = sum(grand_total, na.rm=T), .groups='drop_last') %>% 
  # keep only the top company in each country
  filter(grand_total == max(grand_total)) %>% ungroup() %>% 
  arrange(desc(grand_total))

head(plast_reduce)
```

There are `r length(unique(plast_reduce$parent_company))` total companies in the `r nrow(plast_reduce)` countries listed.

```{r Wrangle}
centroids <- counties %>% st_geometry %>% 
  st_transform(3857) %>% st_centroid %>% st_transform(4326)

county_form <- transmute(counties, county=tools::toTitleCase(County), population=as.numeric(Population), 
  pop_scale=scales::rescale(population, c(0.01,1)), centroid = centroids, type='Colored'
  ) %>% st_set_crs(4326)

# shift sizes around centroids
county_size <- mutate(county_form, geometry = (geometry-centroid)*pop_scale+centroid,
  type='Sized') %>% st_set_crs(4326) 

# replicate the original shape with NA for population so the color fill can animate
county_blank <- mutate(county_form, population = NA, type='Default')

# bind together for gganimate so I can switch between fill states
county_anim <- bind_rows(county_blank, county_form, county_size) %>% 
  mutate(type = factor(type, c("Default",'Colored','Sized')))
```


## TODO
Download one logo
Download county shapefiles
download country xwalk
Try to use it in d3 map
Download all logos if true, if false, dl top ~10 logos
* might also want top polluting countries if using cartogram/bubble map
create spreadsheet of companies + logo paths
Create pollution map
# Visualization

## Spatial Data

Load global countries geojson (downloaded from https://geojson-maps.ash.ms/).
```{r}
geo <- st_read('world_countries.geo.json') %>% 
  st_transform(3857) 

# create centroids
geo_cen <- st_centroid(geo)
```


Visualization
```{r}
r2d3(data=geo_cen, script='plasticMap.js', css='plasticMap.css', dep='topojson.js')
```


How is Kenya's population distributed across counties? Resize the polygons from 1% to 100% of original size based on the population size. Gif included at the top; this is the code that generated it.

```{r narrow_data, eval=FALSE}
anim <- ggplot(county_anim) +
  geom_sf(aes(fill=population)) +
  # animation specs
  transition_states(
    type, transition_length=1, state_length = 2
  )+
  ease_aes('cubic-in-out')+
  enter_fade()+
  # back to ggplot; add counties with no fill so outlines stay consistent
  geom_sf(data=counties, fill=NA) +
  scale_fill_steps(n.breaks=4, low="#bdc9e1", high="#045a8d", labels=scales::comma,
    guide='legend', trans='log10') +
  labs(title="Kenya's Counties", fill='Population') +
  theme_map() +
  theme(
    title=element_text(size=16, color='black')
  )
  
animate(anim, nframes = 20)

```


# Save
```{r eval=FALSE}
anim_save('_tidytuesday/2021-01-19-tidy-tuesday/kenya_county_size.gif', anim)
```

# Review

An obvious limitation to this approach is that a polygon can only go up to 100% of its original size without exceeding its original boundaries. In this map, the smallest county has the largest population, so the visual impact of the shifts is really messy. A possible cleanup strategy would be to make the original polygons to make them smaller, and so that the population-scaled polygons could increase to fit to the original boundaries.